SpARC: Sparse Redundant Calibration

### 2016-09-21 paper.tex
some of the flow of the paper has been specified

 \begin{enumerate}
 \item We need the definition of visibilities as in Liu.
 \item Introduce the array geometery function.
 \item Write down logcal and lincal in matrix form... ?
 \item Short discussion of least squares and jacobian and hessian's. General GN and LM update rules.
 \item Introduce redundant calibration as a least squares problem. We will use this general fact to derive both popular methods.
 \item Propose a possible solution witch leads to lincal. Mention that this approach works as in this form the function is differentiable (a taylor expansion in the 
 parameters exists). Maybe mention that we can also divide the problem into real and imaginary etc...
 \item Show how this relates to lincal for example ---> show lincal is GN.
 \item Now introduce complex optimization ---> Main motivation for switching to the alternative framework is that the the differentials are very simplistic. We wish to show that
 we can derive the method of Chengular.
 \item Do the derivation of Chengular. 
 \item Brief discussion abouth Chengular and SteFCal and Complex Optimization. Here I show that in Oleg's paper he re-derives an algorithm called SteFCal. Stefcal works
 on the basis of alternating direction implicit method. The first signs of achieving a similar algorithm already appeared in Stefan's conference paper in which the alternating
 idea was first proposed. Then I mention Chegular re-derives the expression by using partial derivatives and extends it to redundant. One could also have used the linear alternating
 approach. In an attempt to merge the terminology that has independently develop in the general calibration and redundant calibration literature and to emphasize the close
 relationship between Stefcal and the approach derived by I will use the label Redunandat SteFCal (R-Stefcal) to refer to the NLS method proposed by ... Lastly we mention that similarly
 to how Oleg re-derived stefcal in, we have achieved the same approach.
 \item Faster Exact inverse. A question that Oleg poses in his paper is, does there exist a faster way to take the exact inverse of JhJ? One that is almost linear, and
 implies that we can therefore implement the full LM algorithm. The aim here is of course to reduce the number of iterations that are required to converge by using the 
 full inverse instead which would hopefully provide enough of a speedup to compensate for the more expensive full-inverse. The algorithm we propose is the conjugate 
 gradient method.
 \item We give the images of the HESSIAN of both lincal and the complex method (number of terms). So we can mention that both are sparse and contain diagonal entries that 
 are more significant than 
 \end{enumerate}

>>>>

 \begin{enumerate}
 \item We need the definition of visibilities as in Liu. DEFINE SNR HERE ALREADY together maybe with the sigma value of the noise.
 \item Introduce the array geometery function.
 \item Write down logcal and lincal in matrix form... ?
 \item Short discussion of least squares and jacobian and hessian's. General GN and LM update rules.
 \item Introduce redundant calibration as a least squares problem. We will use this general fact to derive both popular methods.
 \item Propose a possible solution witch leads to lincal. Mention that this approach works as in this form the function is differentiable (a taylor expansion in the 
 parameters exists). Maybe mention that we can also divide the problem into real and imaginary etc...
 \item Show how this relates to lincal for example ---> show lincal is GN.
 \item Now introduce complex optimization ---> Main motivation for switching to the alternative framework is that the the differentials are very simplistic. We wish to show that
 we can derive the method of Chengular.
 \item Do the derivation of Chengular. 
 \item Brief discussion abouth Chengular and SteFCal and Complex Optimization. Here I show that in Oleg's paper he re-derives an algorithm called SteFCal. Stefcal works
 on the basis of alternating direction implicit method. The first signs of achieving a similar algorithm already appeared in Stefan's conference paper in which the alternating
 idea was first proposed. Then I mention Chegular re-derives the expression by using partial derivatives and extends it to redundant. One could also have used the linear alternating
 approach. In an attempt to merge the terminology that has independently develop in the general calibration and redundant calibration literature and to emphasize the close
 relationship between Stefcal and the approach derived by I will use the label Redunandat SteFCal (R-Stefcal) to refer to the NLS method proposed by ... Lastly we mention that similarly
 to how Oleg re-derived stefcal in, we have achieved the same approach.
 \item Faster Exact inverse. A question that Oleg poses in his paper is, does there exist a faster way to take the exact inverse of JhJ? One that is almost linear, and
 implies that we can therefore implement the full LM algorithm. The aim here is of course to reduce the number of iterations that are required to converge by using the 
 full inverse instead which would hopefully provide enough of a speedup to compensate for the more expensive full-inverse. The algorithm we propose is the conjugate 
 gradient method.
 \item We give the images of the HESSIAN of both lincal and the complex method (number of terms). So we can mention that both are sparse and contain diagonal entries that 
 are more significant than the off-diagonal entries. What linear inversion approach can take advantage of both these phenomenon. One such technique is 
 cg. 
 \item Briefly discuss CG and how its computationally bounded by its condition number and its sparsity (how does the diagonal play a role).
 \item Simulation description
 \item Will CG improve things?
 \item Now first discuss the condition
 number of the Hessian before and after pre-conditioning (pre-codnitioning can only be applied if a good inverse of a matrix is known, if it is known then it can improve 
 the spectral condition number of a matrix. We present here the kappa and iteration number graphs for the HEXAGONAL layout. Although the
 \item Now we discuss the sparsity results. 
 \item Provide a table that theoretical compares R-StEFCal and SPARC.
 \item Number of outerloop iterations. 
 \item Timing results.
 \item Accuracy results.
 \item Maybe some freq simulations.
 \end{enumerate}
